Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-10-31 paper/paper.tex
write on participant demographics

In comparison with a traditional web-based form, Cyberlioz offers a more intuitive and playful user experience, while limiting the acquisition of similarity judgments to a moderate duration of $30$ to $60$ minutes for each participant.
In May and June 2016, we recruited volunteers to use Cyberlioz on their own computers, via a web browser, and equipped with a pair of earphones.
To this end, we publicized this study on the internal mailing list of students at CNSMDP, as well as two international mailing lists for research in music audio processing: AUDITORY  and ISMIR Community.\footnote{
For more information about these mailing lists, please visit:
\url{http://www.auditory.org/} and \url{http://ismir.net/}}
Within two months, $K=31$ participants accessed Cyberlioz and completed the task.
We did not collect personal information on the age, gender, nor musical background of participants.

>>>>

In comparison with a traditional web-based form, Cyberlioz offers a more intuitive and playful user experience, while limiting the acquisition of similarity judgments to a moderate duration of $30$ to $60$ minutes for each participant.
In May and June 2016, we recruited volunteers to use Cyberlioz on their own computers, via a web browser, and equipped with a pair of earphones.
To this end, we publicized this study on the internal mailing list of students at CNSMDP, as well as two international mailing lists for research in music audio processing: AUDITORY  and ISMIR Community.\footnote{
For more information about these mailing lists, please visit:
\url{http://www.auditory.org/} and \url{http://ismir.net/}}
Within two months, $K=31$ participants accessed Cyberlioz and completed the task.

We did not collect personal information on the age, sex, nor musical background of participants.
This is because the goal of our perceptual study is to build a consensus of similarity judgments, rather than to compare demographic subgroups.
We note that the relatively small size of our cohort ($K=31$) lacks the statistical power to carry out such a comparison.
In particular, we leave the important question of the effect of musical training on the  as future work.
